More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-05-03 2016-Weak-FH-Bisim/WeakBisim.tex
Open transitions are identified modulo logical equivalence on their predicate.
mark ot eq done

Ludo
\begin{itemize}
\item[x] rewrite Tr2 and open transition with actions
\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
\item[x] $\beta$ ou $b$
\item[x] propager Tr2 dans l annexe
\item add simple equivalence on OT
\item[x] explain the 2 level logic
\end{itemize}
=== 18 Avril
\medskip

@@

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
	equations 
	that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

>>>>

Ludo
\begin{itemize}
\item[x] rewrite Tr2 and open transition with actions
\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
\item[x] $\beta$ ou $b$
\item[x] propager Tr2 dans l annexe
\item[x] add simple equivalence on OT -- fait a minima 
\item[x] explain the 2 level logic
\end{itemize}
=== 18 Avril
\medskip

@@

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
	equations 
	that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\subst{x_k\gets e_k}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}
